### 2021-05-25 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Add comparisons between Markov and DES
Include violinplots of waiting time, blocking time and proportion
within target time. The violinplots show the differences between
Markov values and simulated values.

>>>>

Additional details on the blocking time formula 
(\ref{eq:algebraic_blocking_time}) can be found in appendix 
\ref{sec:appendix_mean_blocking}. 
Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between Markov chains and discrete event simulation of the blocking time of
type 2 individuals.

\begin{figure}[ht]
    \centering
    \scalebox{0.7}{\includegraphics{
        imgs/markov_vs_des/blocking_time/main.pdf
    }}
    \caption{
        Comparison of mean blocking time between values obtained from the Markov
        chain formulas and values obtained from simulation. The simulation 
        was ran 100 times and the recorded mean blocking time at each iteration
        is used to populate the violin plots.
    }
    \label{fig:markov_vs_des_blocking_time_comparison}
\end{figure}

### 2021-05-25 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Add comparisons between Markov and DES
Include violinplots of waiting time, blocking time and proportion
within target time. The violinplots show the differences between
Markov values and simulated values.

>>>>

Appendix \ref{sec:appendix_mean_waiting} gives more details on the recursive
formula that equations (\ref{eq:closed_form_waiting_type_1}),
(\ref{eq:closed_form_waiting_type_2}) and (\ref{eq:overall_waiting_time})
originate from.

Figure \ref{fig:markov_vs_des_waiting_time_comparison} shows a comparison 
between the calculated mean waiting time using Markov chains and the simulated waiting time using discrete event simulation.

\begin{figure}[ht]
    \centering
    \scalebox{0.7}{\includegraphics{
        imgs/markov_vs_des/waiting_time/main.pdf
    }}
    \caption{
        Comparison of mean waiting time between values obtained from the Markov
        chain formulas and values obtained from simulation. The simulation 
        was ran 100 times and the recorded mean waiting time at each iteration
        is used to populate the violin plots.
    }
    \label{fig:markov_vs_des_waiting_time_comparison}
\end{figure}
